Designing Turk Experiments for Visual Statistical Inference

### 2013-07-22 paper_turk.tex
upto accepting and rejecting (4.2)

\section{Managing Turk Task}\label{sec:turk_task} \cite{turk} Mechanical Turk website provides various features that are helpful to maintain and organize the task and manage the workers. Creating, posting, accepting or rejecting tasks and processing payment are done from the MTurk system. It is also possible to screen out workers as needed. For example, none will be interested to recruit people who have a very bad reputation. This information can be obtained from each worker's previous work history of total number of accepted task out of total number of submitted task. The web application we developed is for presenting lineups in a flexible way the researcher may want  as per the experimental design and collecting data. To get people to the web application we need to design a turk task in MTurk system.

@@

\item The number of worker to recruit has to be provided so that the turk task remain open until specific number of people do the task. This is related to the sample size of the data we intend to collect on each lineup.

>>>>

\section{Managing Turk Task}\label{sec:turk_task} \cite{turk} Mechanical Turk website provides various features that are helpful to maintain and organize the task and manage the workers. Creating, posting, accepting or rejecting tasks and processing payment can be done from the MTurk system. It is also possible to screen out workers as needed. For example, none will be interested to recruit people who have a very bad reputation. This information can be obtained from each worker's previous work history of total number of accepted task out of total number of submitted task. The web application we developed is for presenting lineups in a flexible way the researcher may want  as per the experimental design and collecting data. To get people to the web application we need to design a turk task in MTurk system.

@@

\item The number of workers to recruit has to be provided so that the turk task remains open until some specific number of people do the task. This is related to the sample size of the data we intend to collect on each lineup.
